The Hyperedge Event Model

### 2018-11-16 paper/revision1/ba-sample.tex

	Processes that arise as time-stamped directed interactions are common in the social, natural, and phyiscal sciences. The data produced by such processes can be represented as dynamic directed networks---an object that has given rise to the development of several statistical model families. For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize that network evolutions occur as the senders decide to create or remove an edge from the existing network, one edge at a time. Event-based network models \citep{Butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events. This family of models is flexible enough to account for the many ways in which past network structures beget future ones---e.g., if node $i$ directed a tie to node $j$ recently, then node $j$ will direct one to node $i$ in the near future---and useful for understanding the traits and behaviours that are predictive of interactions.

@@

	The hyperedge event model (HEM) specifies a generative process for $E$ unique hyperedge events that occur between $V$ number of nodes. A single hyperedge event is indexed by $e \in [E]$---where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$---and consists of three components: the sender $s_e \in [V]$, an indicator vector of receivers $\boldsymbol{r}_e$---where the element 1 indicates ``receiving" the hyperedge event $e$ and 0 otherwise---and the timestamp $t_e \in (0, \infty)$. For simplicity, we assume that events are ordered by time such that $t_e \leq t_{e+1}$. While the model can be applied to two types of hyperedge events---events involving (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast). One notable feature of our generative process is that we draw auxiliary variables that serve as candidate data. Data is generated from the HEM through a sampling process applied to the auxiliary variables. The auxiliary variables drawn for event $e$ include, for each possible sender $i \in [V]$, a time increment from event $e-1$ at which sender $i$ would create event $e$, and an $V-1$ length vector indicating which nodes would be the receivers of event $e$ if it were directed by sender $i$.  The data generated for event $e$ under the HEM corresponds to the sender that would create event $e$ the soonest---at the smallest time increment from event $e-1$. The receivers of event $e$ generated under the HEM correspond to those receivers toward which the sender with the minimum time increment would have directed event $e$. We explain these steps in more detail below. Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $V=5$. For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers). Throughout the paper, we use the notation $y_{iej}$ to imply ``sender $i$ directs an event $e$ to receiver $j$," where $y$ can be any parameter or covariate introduced in the HEM. When it is relevant to sender or receiver only, we use $y_{ie}$ and $y_{ej}$ to imply ``sender $i$ of an event $e$" and ``receiver $j$ of event $e$," respectively. ~\looseness=-1

@@

Though the HEM, based on our knowledge of the literature, is unique in modeling hyperedge events in continuous time, we build our model using features inspired by many of the existing models for dynamic network data. First, the features that govern which receivers are selected by a given sender are defined using subgraph configuration counts (e.g., the number of triangles formed through sending the tie, the number of previous hyperedges that would be reciprocated by the tie). The HEM's use of subgraph configuration formation follows a similar process underlying network change in the the continuous-time event model proposed by \cite{PerryWolfe2012} as well as the relational event model \citep{Butts2008}, and is also related to the subgraph completion processes used to model discrete-time network change in the temporal ERGM \citep{hanneke2010discrete}. Second, the use of candidate receivers as a mechanism through which continuous network change is modeled is related to the use of latent changes between snapshot network observations in the stochastic actor oriented model (SAOM) by \cite{snijders1996stochastic}.  Third, also like the SAOM, the HEM includes separate sets of parameters that are used to model event timing and edge generation. Though unique in modeling hyperedges, the HEM is grounded in existing continuous-time models of networks, ERGM-style models, and the SAOM.

@@

				\STATE update $u_{iej}$ using Gibbs update ---equation (\ref{eqn:latentreceiver})

@@

There are many MH routines in the literature. Which type of MH do you consider? What is the proposal distribution? What about the acceptance rate? Is there any smart proposal in this case which helps in increasing the acceptance rate.

@@

	We evaluated the models' ability to predict out-of-sample events and timestamps on Montgomery County email data. We generated a train--test split of the data by randomly selecting 10\% of senders, receivers, and timestamp variables to be held out. Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables. Algorithm \ref{alg:PPE} outlines this procedure in detail. We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments, by repeating the predictive assessments$N=500$ times where we make new predictions each time for the fixed held out data. We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}. First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{s_ee}$ in Algorithm \ref{alg:PPE}. We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{s_{e}e} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{s_{e}e}$---across the missing emails. The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $V$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model. Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $e$ and $j$ with $r_{ej}$=NA) by taking the harmonic mean of precision and recall:

@@

				\STATE compute $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$, where \\$\pi_{ie}=\Big(f_{\tau}(\tau_{ e}; \mu_{i e}, \sigma_\tau^2)\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{ e}; \mu_{i^\prime  e}, \sigma_\tau^2) \big)\Big) \times$

@@

				where $p_{ej}=\frac{\exp(\lambda_{iej})}{\exp(\lambda_{iej})+\text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )}$ %as defined in equation (\ref{eqn:latentreceiver})

@@

				\STATE draw ${\tau}_e$ from its conditional distribution using importance sampling, %from equation (\ref{eqn:latenttime}) (without the product term) 
				where $P({\tau}_e|\, \cdot)\propto \Big(f_{\tau}(\tau_{e}; \mu_{s_{e} e}, \sigma_\tau^2)\times \prod_{i\neq s_{e}}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2)\big)\Big) \times $%\footnote{we need to specify appropriate proposal distribution such as $g \sim \mbox{halfcauchy}(5)$}

@@

			\newpage
			\bibliographystyle{ba}
			\bibliography{baHEM}

	\section*{Appendix}
	\subsection*{Appendix A: Alternative generative process} \label{appendix:alternativeGP}
	\begin{algorithm}[H]
		\SetAlgoLined
		\caption{Generative process: one receiver and one or more senders}
		\begin{algorithmic}
			\STATE \textbf{Input}: number of events and nodes $(E, V)$, covariates $(\boldsymbol{x}, \boldsymbol{z})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
			\vskip 0.1in				
			\FOR{$e=1$ to $E$}
			\FOR{$j=1$ to $V$}
			\FOR{$i=1$ to $V$ ($i \neq j$)}
			\STATE	set $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$
			\ENDFOR
			\STATE	draw $\boldsymbol{u}_{je}  \sim
			\mbox{MB}_G(\boldsymbol{\lambda}_{je})$
			\STATE		set $\mu_{je} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{z}_{je})$
			\STATE		draw $\tau_{je} \sim f_\tau(\mu_{je}, \sigma_\tau^2)$
			\ENDFOR
			\IF {$n \geq 2$ tied events} 
			\STATE	set ${r}_e,\ldots, r_{e+n-1}=\mbox{argmin}_{j}(\tau_{je})$
			\STATE	set $\boldsymbol{s}_e=\boldsymbol{u}_{r_e e},\ldots,\boldsymbol{s}_{e+n-1}=\boldsymbol{u}_{r_{e+n-1} e}$
			\STATE	set $t_e, \ldots, t_{e+n-1}=t_{e-1} + \min_j\tau_{je}$
			\STATE		jump to $e = e+n$
			\ELSE
			\STATE	set ${r}_e = \mbox{argmin}_{j}(\tau_{je}) $
			\STATE	set $\boldsymbol{s}_e= \boldsymbol{u}_{r_e e}$
			\STATE	set $t_e =t_{e-1} + \min_j\tau_{je}$
			\ENDIF
			\ENDFOR
		\end{algorithmic}
		\label{alg:generative2}
	\end{algorithm}
	\subsection*{Appendix B: Normalizing constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $i$ selecting the binary receiver vector $\boldsymbol{u}_{ie}$ as
	\begin{equation*} 
		\begin{aligned}
			& \Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{C(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ie} \rVert_1 > 0)\big) + \sum_{j \neq i} \lambda_{iej}u_{iej} \Big),
		\end{aligned}
	\end{equation*}
	where $\lambda_{iej}$ is a linear combination of receiver selection features---i.e., $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$---as defined in Secton \ref{subsec: Tie}.

>>>>

	Processes that arise as time-stamped directed interactions are common in the social, natural, and phyiscal sciences. The data produced by such processes can be represented as dynamic directed networks---an object that has given rise to the development of several statistical model families. For example, stochastic actor-oriented models (SAOMs) \citep{snijders1996stochastic,snijders2007modeling} characterize that network evolutions occur as the senders decide to create or remove an edge from the existing network, one edge at a time. Event-based network models \citep{butts2008,Vu2011,hunter2011dynamic,PerryWolfe2012} provide a general framework for modeling the realization of edges that occur as instances in continuous time streams of events. This family of models is flexible enough to account for the many ways in which past network structures beget future ones---e.g., if node $i$ directed a tie to node $j$ recently, then node $j$ will direct one to node $i$ in the near future---and useful for understanding the traits and behaviours that are predictive of interactions.

@@

	The hyperedge event model (HEM) specifies a generative process for $E$ unique hyperedge events that occur between $V$ number of nodes. A single hyperedge event is indexed by $e \in [E]$---where $[E]$ denotes a categorical set with $E$ levels $[E] = \{1,\ldots,E\}$---and consists of three components: the sender $s_e \in [V]$, an indicator vector of receivers $\boldsymbol{r}_e$---where the element 1 indicates ``receiving" the hyperedge event $e$ and 0 otherwise---and the timestamp $t_e \in (0, \infty)$. For simplicity, we assume that events are ordered by time such that $t_e \leq t_{e+1}$. While the model can be applied to two types of hyperedge events---events involving (1) one sender and one or more receivers, and (2) one or more senders and one receiver---here we only present the generative process for those involving one sender and one or more receivers (i.e., multicast). One notable feature of our generative process is that we draw auxiliary variables that serve as candidate data. Data is generated from the HEM through a sampling process applied to the auxiliary variables. The auxiliary variables drawn for event $e$ include, for each possible sender $i \in [V]$, a time increment from event $e-1$ at which sender $i$ would create event $e$, and an $V-1$ length vector indicating which nodes would be the receivers of event $e$ if it were directed by sender $i$.  The data generated for event $e$ under the HEM corresponds to the sender that would create event $e$ the soonest---at the smallest time increment from event $e-1$. The receivers of event $e$ generated under the HEM correspond to those receivers toward which the sender with the minimum time increment would have directed event $e$. We explain these steps in more detail below. Figure \ref{figure:diagram} presents an illustrative example on how the $e^{\textrm{th}}$ event is generated, assuming $t_{e-1} = 0$ and $V=5$. For hyperedge events that involve one receiver and one or more senders, we treat $s_e$ to be an indicator vector of senders $\boldsymbol{s}_e$ and $r_e$ to be the single receiver, and then follow the alternative generative process provided in Appendix A, which we derive as a simple reversal of the process used for multicasts (i.e., one sender and multiple receivers). Throughout the paper, we use the notation $y_{iej}$ to imply ``sender $i$ directs an event $e$ to receiver $j$," where $y$ can be any parameter or covariate introduced in the HEM. When it is relevant to sender or receiver only, we use $y_{ie}$ and $y_{ej}$ to imply ``sender $i$ of an event $e$" and ``receiver $j$ of event $e$," respectively. Similarly, we use $y_e$ to denote the quantity associated with ``event $e$".~\looseness=-1

@@

Though the HEM, based on our knowledge of the literature, is unique in modeling hyperedge events in continuous time, we build our model using features inspired by many of the existing models for dynamic network data. First, the features that govern which receivers are selected by a given sender are defined using subgraph configuration counts (e.g., the number of triangles formed through sending the tie, the number of previous hyperedges that would be reciprocated by the tie). The HEM's use of subgraph configuration formation follows a similar process underlying network change in the the continuous-time event model proposed by \cite{PerryWolfe2012} as well as the relational event model \citep{butts2008}, and is also related to the subgraph completion processes used to model discrete-time network change in the temporal ERGM \citep{hanneke2010discrete}. Second, the use of candidate receivers as a mechanism through which continuous network change is modeled is related to the use of latent changes between snapshot network observations in the stochastic actor oriented model (SAOM) by \cite{snijders1996stochastic}.  Third, also like the SAOM, the HEM includes separate sets of parameters that are used to model event timing and edge generation. Though unique in modeling hyperedges, the HEM is grounded in existing continuous-time models of networks, ERGM-style models, and the SAOM.

@@

				\STATE update $u_{iej}$ using Gibbs update---equation (\ref{eqn:latentreceiver})

@@

There are many MH routines in the literature. Which type of MH do you consider? What about the acceptance rate? Is there any smart proposal in this case which helps in increasing the acceptance rate.

@@

	We evaluated the models' ability to predict out-of-sample events and timestamps on Montgomery County email data. We generated a train--test split of the data by randomly selecting 10\% of senders, receivers, and timestamp variables to be held out. Our model then imputed these missing variables during inference, sampling them from their conditional posterior along with the other latent variables. One important point is that our covariates $\boldsymbol{x}$ and $\boldsymbol{z}$
depend on the observed interaction data in the last 7 days, as written in Section \ref{subsec:Covariates_email}, hence the observations $ \{ (s_e, \boldsymbol{r}_e, t_e)\}_{e=1}^E$ are not conditionally independent given the model parameters. If the sender of event $e$ is missing, we draw from the categorical distribution using the sender probability vector $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$. As a result, the conditional distribution for the missing observations $s_e$, $r_{ej}$, and $t_e$ should depend on $ \{ (s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime})\}_{e^\prime \in m_e}$, where $m_e = (t_e, t_e+\mbox{7 days}]$. In particular, if the sender $s_e$ is missing, then we draw from the categorical distribution using the sender probability $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$, where $\pi_{ie}$ follows
		\begin{equation}
		\begin{aligned}
\pi_{ie}=\Big(f_{\tau}(\tau_{ e}; \mu_{i e}, \sigma_\tau^2)\times \prod_{i^\prime\neq i}\big(1-F_{\tau}(\tau_{ e}; \mu_{i^\prime  e}, \sigma_\tau^2) \big)\Big) \times \prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|s_{e}=i)
		\end{aligned}
				\label{eqn:missingsender}
		\end{equation}
		with $L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|s_{e}=i)$ denoting the joint likelihood of $(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime})$ conditioned on the covariates $\boldsymbol{x}_{e^\prime}$ and $\boldsymbol{z}_{e^\prime}$ calculated assuming $s_{e}=i$. Here, the term $\prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime})$ is proportional to the multiplication of equation (\ref{eqn:latentedge}) and equation (\ref{eqn:latenttime}) (or equation (\ref{eqn:latenttime2})), with the product over $e=1,\ldots,E$ replaced by $\{e^\prime:t_{e^\prime} \in m_e\}$. Similarly, if the $j$th receiver indicator $r_{ej}$ is missing, we sample from Bernoulli distribution where
				\begin{equation}
				\begin{aligned}
			P(r_{ej}=1)&=\exp(\lambda_{iej})\times \prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|r_{ej}=1),\\
			P(r_{ej}=0) &= \text{I}(\lVert\boldsymbol{u}_{ie\backslash j}\rVert_1 > 0 )\times \prod_{e^\prime: t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|r_{ej}=0).
				\end{aligned}
								\label{eqn:missingreceiver}
				\end{equation}
	Finally, when the timestamp $t_e$ is missing, we draw the time increment $\tau_e$ via importance sampling using the proposal distribution $g \sim \mbox{halfcauchy}(5)$, where its conditional distribution follows
			\begin{equation}
			\begin{aligned}
P({\tau}_e|\, \cdot)\propto \Big(f_{\tau}(\tau_{e}; \mu_{s_{e} e}, \sigma_\tau^2)\times \prod_{i\neq s_{e}}\big(1-F_{\tau}(\tau_{e}; \mu_{ie}, \sigma_\tau^2)\big)\Big) \times\prod_{e^\prime:t_{e^\prime} \in m_e} L(s_{e^\prime}, \boldsymbol{r}_{e^\prime}, t_{e^\prime}|\tau_{e}).
			\end{aligned}
							\label{eqn:missingtime}
			\end{equation}
	Algorithm \ref{alg:PPE} outlines this procedure.

	We compare the predictive performance of two versions of our model, each with a different timing distribution over the time increments, by repeating the predictive assessments $N=500$ times where we make new predictions each time for the fixed held out data. We summarize the results of prediction experiments for missing senders, receivers, and timestamps in Figure \ref{figure:PPEresults}. First, we compare the posterior probability of correct senders for each of the missing emails $\{e:s_e=\mbox{NA}\}$, which corresponds to $\pi_{s_ee}$ in Algorithm \ref{alg:PPE}. We call this measure the ``correct sender posterior probability." In Figure \ref{subfigure:PPEresults1}, we display boxplots for the distribution of mean correct sender posterior probability---i.e., $\hat{\pi}_{s_{e}e} = \frac{1}{N}\sum_{n=1}^N \pi^{(n)}_{s_{e}e}$---across the missing emails. The results show that both log-normal and exponential distributions achieve better predictive performance for missing senders compared to what is expected under random guess (i.e., choose one out of $V$ possible senders $=1/18$), with the log-normal model showing better performance than the exponential model. Secondly, since the receiver vector is binary, we compute $F_1$ scores for missing receiver indicators (i.e., all $e$ and $j$ with $r_{ej}$=NA) by taking the harmonic mean of precision and recall:

@@

				\STATE compute $\boldsymbol{\pi}_e = (\pi_{1e},\ldots,\pi_{Ve})$---equation (\ref{eqn:missingsender})

@@

				where $p_{ej}=\frac{P(r_{ej}=1)}{P(r_{ej}=1)+P(r_{ej}=0)}$---equation (\ref{eqn:missingreceiver})

@@

				\STATE draw ${\tau}_e$ using importance sampling---equation (\ref{eqn:missingtime})%from equation (\ref{eqn:latenttime}) (without the product term) 

@@

			\newpage
			\bibliographystyle{ba}
			\bibliography{baHEM}	
	\section*{Appendix}
	\subsection*{Appendix A: Alternative generative process} \label{appendix:alternativeGP}
	\begin{algorithm}[H]
		\SetAlgoLined
		\caption{Generative process: one receiver and one or more senders}
		\begin{algorithmic}
			\STATE \textbf{Input}: number of events and nodes $(E, V)$, covariates $(\boldsymbol{x}, \boldsymbol{z})$, and coefficients $(\boldsymbol{b}, \boldsymbol{\eta})$
			\vskip 0.1in				
			\FOR{$e=1$ to $E$}
			\FOR{$j=1$ to $V$}
			\FOR{$i=1$ to $V$ ($i \neq j$)}
			\STATE	set $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$
			\ENDFOR
			\STATE	draw $\boldsymbol{u}_{je}  \sim
			\mbox{MB}_G(\boldsymbol{\lambda}_{je})$
			\STATE		set $\mu_{je} = g^{-1}(\boldsymbol{\eta}^\top \boldsymbol{z}_{je})$
			\STATE		draw $\tau_{je} \sim f_\tau(\mu_{je}, \sigma_\tau^2)$
			\ENDFOR
			\IF {$n \geq 2$ tied events} 
			\STATE	set ${r}_e,\ldots, r_{e+n-1}=\mbox{argmin}_{j}(\tau_{je})$
			\STATE	set $\boldsymbol{s}_e=\boldsymbol{u}_{r_e e},\ldots,\boldsymbol{s}_{e+n-1}=\boldsymbol{u}_{r_{e+n-1} e}$
			\STATE	set $t_e, \ldots, t_{e+n-1}=t_{e-1} + \min_j\tau_{je}$
			\STATE		jump to $e = e+n$
			\ELSE
			\STATE	set ${r}_e = \mbox{argmin}_{j}(\tau_{je}) $
			\STATE	set $\boldsymbol{s}_e= \boldsymbol{u}_{r_e e}$
			\STATE	set $t_e =t_{e-1} + \min_j\tau_{je}$
			\ENDIF
			\ENDFOR
		\end{algorithmic}
		\label{alg:generative2}
	\end{algorithm}
	\subsection*{Appendix B: Normalizing constant of MB$_{G}$}\label{appendix: non-empty Gibbs measure}
	Our probability measure ``MB$_{G}$''---the multivariate Bernoulli distribution with non-empty Gibbs measure---defines the probability of sender $i$ selecting the binary receiver vector $\boldsymbol{u}_{ie}$ as
	\begin{equation*} 
		\begin{aligned}
			& \Pr(\boldsymbol{u}_{ie}|\,\boldsymbol{b}, \boldsymbol{x}_{ie}) = \frac{1}{C(\boldsymbol{\lambda}_{ie})}\exp\Big(\mbox{log}\big(\text{I}(\lVert \boldsymbol{u}_{ie} \rVert_1 > 0)\big) + \sum_{j \neq i} \lambda_{iej}u_{iej} \Big),
		\end{aligned}
	\end{equation*}
	where $\lambda_{iej}$ is a linear combination of receiver selection features---i.e., $\lambda_{iej} = {\boldsymbol{b}}^{\top}\boldsymbol{x}_{iej}$---as defined in Secton \ref{subsec: Tie}.
